Openness and Computational Reproducibility in Plant Pathology: Where do we Stand and a Way Forward

### 2022-06-16 analysis/paper/paper.Rmd
format code chunk

invisible(
  lapply(
    packages,
    library,
    character.only = TRUE
  )
)

@@

load(system.file("extdata",
                 "m_f1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_f2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_g1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_g2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))

load(system.file("extdata",
                 "m_h1.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h1_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
load(system.file("extdata",
                 "m_h2_report.Rda",
                 package = "Reproducibility.in.Plant.Pathology",
                 mustWork = TRUE))
```

>>>>

invisible(lapply(packages,
                 library,
                 character.only = TRUE))

@@

load(
  system.file(
    "extdata",
    "m_f1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_f2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

load(
  system.file(
    "extdata",
    "m_g1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_g2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)

load(
  system.file(
    "extdata",
    "m_h1.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h1_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
load(
  system.file(
    "extdata",
    "m_h2_report.Rda",
    package = "Reproducibility.in.Plant.Pathology",
    mustWork = TRUE
  )
)
```
